Constant-round Blind Classical Verification of Quantum Sampling

### 2022-02-28 blind.tex
Fix wording

To resolve the issue, we let the verifier switch to a fresh new key for each round of the protocol.\footnote{
An alternative strategy is to assume circuit privacy of $\QHE$. This turns out to require many additional properties such as \emph{malicious} circuit privacy, efficient simulation and extraction, multi-hop evaluation, and classical $\QEval$ on classical ciphertexts and circuits. While existing constructions such as \cite{circuit-private-qfhe} achieves many of these properties, we are not sure if any constructions satisfy all our requirements.}
For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$.
Note that a fresh key pair is necessary here to ensure blindness, as decrypting uses information from the secret key.
Since the verifier $\Vblind$ only  sends fresh ciphertexts to $\Pblind$, this avoids the issue of circuit privacy. Additionally, to allow $\Pblind$ to homomorphically evaluate its next message, $\Vblind$ needs to encrypt the previous secret key $sk$ under the new public key $pk'$ and send it along with $pk'$ to $\Pblind$. This allows the prover to homomorphically convert ciphertexts under key $pk$ to ciphertexts under key $pk'$. By doing so, we show that for any cheating prover $\Pblindstar$, the interaction $(\Pblindstar, \Vblind)$ indeed simulates a valid interaction of $(\Pstar, V)$ for some cheating $\Pstar$, and hence the soundness of $\Pi$ implies the soundness of the compiled protocol. Finally, for the issue of the prover sending invalid ciphertexts, we note that this is not an issue if the decryption never fails, which can be achieved by simply let the decryption algorithm output a default dummy message (e.g., $0$) when it fails.

>>>>

To resolve the issue, we let the verifier switch to a fresh new key for each round of the protocol.\footnote{
An alternative strategy is to assume circuit privacy of $\QHE$. This turns out to require many additional properties such as \emph{malicious} circuit privacy, efficient simulation and extraction, multi-hop evaluation, and classical $\QEval$ on classical ciphertexts and circuits. While existing constructions such as \cite{circuit-private-qfhe} achieves many of these properties, we are unsure if any construction satisfies all our requirements.}
For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$.
Note that a fresh key pair is necessary here to ensure blindness, as decrypting uses information from the secret key.
Since the verifier $\Vblind$ only  sends fresh ciphertexts to $\Pblind$, this avoids the issue of circuit privacy. Additionally, to allow $\Pblind$ to homomorphically evaluate its next message, $\Vblind$ needs to encrypt the previous secret key $sk$ under the new public key $pk'$ and send it along with $pk'$ to $\Pblind$. This allows the prover to homomorphically convert ciphertexts under key $pk$ to ciphertexts under key $pk'$. By doing so, we show that for any cheating prover $\Pblindstar$, the interaction $(\Pblindstar, \Vblind)$ indeed simulates a valid interaction of $(\Pstar, V)$ for some cheating $\Pstar$, and hence the soundness of $\Pi$ implies the soundness of the compiled protocol. Finally, for the issue of the prover sending invalid ciphertexts, we note that this is not an issue if the decryption never fails, which can be achieved by simply let the decryption algorithm output a default dummy message (e.g., $0$) when it fails.
